% AnthonyChangResume

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{ragged2e}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\begin{document}
\begin{center}
\textbf{\LARGE{Anthony Chang}}

Austin, TX • anthony.chang@utexas.edu • 281-961-4501\\
https://www.linkedin.com/in/anthony-chang1/ • https://github.com/MasterSushiChef
\end{center}

\section{Education}
\textbf{University of Texas at Austin} \hfill \textit{Austin, TX}\\
\begin{itemize}[noitemsep, topsep=0pt]
  \item \textbf{Major:} Bachelor of Science in Aerospace Engineering; GPA: 3.88 \hfill \textit{Aug. 2018 -- Dec. 2021}\\
  \item \textbf{Intended Certificate:} Computational Engineering\\
\end{itemize}
%\bigskip
\textbf{\small{Clements High School}} \hfill \textit{Aug. 2014 -- May 2018}
\begin{itemize}[noitemsep, topsep=0pt]
  \item \small{National Merit Finalist, National AP Scholar}
\end{itemize}

\section{Experience}
\textbf{Fujitsu Network Communications} \hfill Richardson, TX\\
\textit{Software Development Intern} \hfill \textit{Jun. 2019 -- Aug. 2019}\\
\begin{itemize}[noitemsep, topsep=0pt]
  \item Created a Python desktop app with a drag and drop GUI to generate equipment configuration templates
  \item Improved the efficiency of internal testing of telecommunications equipment by reducing communication and user 
  input errors % Includes features of GUI???
  \item Worked with mentors to solidify design and feature requirements % More soft related skills???
\end{itemize}
\textbf{UAV Austin} \hfill Austin, TX\\
\textit{Infrastructure Team Lead} \hfill \textit{Aug. 2019 -- present}\\
\begin{itemize}[noitemsep, topsep=0pt]
  \item Teaching people xd % What do
\end{itemize}
\textit{Infrastructure Team Member} \hfill \textit{Aug. 2018 -- Jun. 2019}\\
\begin{itemize}[noitemsep, topsep=0pt]
  \item Created a service to log continuous flight data using InfluxDB then integrated with a Grafana dashboard
  \item Collaborated in pairs to develop an ICMP ping service to ping devices on the UAV directly
  \item Experience in project development sprints using Agile methodologies and containerized services 
  \item Tweaked service to allow for user control of upload rates of flight data to competition servers % on the chopping block
  \item One of 11 members on the competition team % more descriptive?
\end{itemize}
\textbf{Self-Employed} \hfill Sugar Land, TX\\
\textit{High School Math Tutor} \hfill \textit{Mar. 2018 -- Jun. 2018}\\
\begin{itemize}[noitemsep, topsep=0pt]
  \item Tutored 5 high schoolers individually in in SAT prep, Pre-AP Algebra II, AP Physics I, and Geometry
  \item Raised tutee’s SAT math section score by 120 points
  \item Improved a tutee’s Algebra II grade from a 78 to an 85 over the course of 4 weeks
\end{itemize}
\section{Projects}
\textbf{Disaster Watch Chrome Extension}\\
\begin{itemize}[noitemsep, topsep=0pt] %not clear what this is
  \item Implemented backend of simple Chrome extension created at a small university hackathon using Node.js
  \item Collaborated with two other team members to create a basic HTML/CSS frontend
  \item Intefaced with Google Maps API to determine possible user danger during a flood event
\end{itemize}
\textbf{RecipeWriter Recurrent Neural Network}\\
\begin{itemize}[noitemsep, topsep=0pt]
  \item Created a neural network capable of generating recipes using Java in IntelliJ IDEA with Maven
  \item Utilized deep learning \& multi-dimensional matrix libraries to create a basic recurrent neural network
  \item Applied knowledge from multivariate and vector calculus to understand key concepts
\end{itemize}
\section{Qualifications/Skills}
\textbf{Computer languages:} Python, C++, Javascript, Java, MATLAB, HTML\\
\textbf{Technologies:} Node.js, Git, InfluxDB, Grafana, Docker, Solidworks\\
\textbf{Languages:} Chinese, Japanese\\
\end{document}
